Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2): Submission, Peer-Review, and Sorting Process, and Results

### 2014-11-11 WSSSPE2_preworkshop_report/WSSSPE2_review_report.tex
moving the last uncategorized paper to a category
small changes
fixing Karen's affil

\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
Karen Cranston$^{(affil?)}$, Manish Parashar$^{(4)}$, David Proctor$^{(affil?)}$, \\
Matthew Turk$^{(2)}$, Colin C. Venters$^{(6)}$, Nancy Wilkins-Diehr$^{(5)}$}

@@

\thanks{{}$^{(4)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}

\thanks{{}$^{(5)}$ University of California-San Diego, San Diego, CA, USA}

@@

@@

\todo{fix affils}

@@

The organizers then chose the soft with five groups as the one that felt most meaningful, then decided on names for the five groups, namely:
\begin{itemize}
\item Exploring Sustainability
\item Software Development Experiences
\item Policy
\item Reproducibility \& Reuse \& Sharing
\item Code Testing \& Code Review
\end{itemize}

@@

The contributed papers that will be discussed at the workshop follow, listed by \todo{update when possible - current list is just alphabetic order, not grouped}

@@

\item Software Development Experiences
\begin{itemize}
\item Jordan Adams, Sai Nudurupati, Nicole Gasparini, Daniel Hobley, Eric Hutton, Gregory Tucker and Erkan Istanbulluoglu. Landlab: Sustainable Software Development in Practice ~\cite{wssspe2_adams}
\item Alice Allen and Judy Schmidt. Looking before leaping: Creating a software registry~\cite{wssspe2_allen}
\item Carl Boettiger, Ted Hart, Scott Chamberlain and Karthik Ram. Building software, building community: lessons from the {ROpenSci} project~\cite{wssspe2_boettiger}
\item Michael R. Crusoe and C.Titus Brown. Channeling community contributions to scientific software: a hackathon experience~\cite{wssspe2_crusoe}
\item Yolanda Gil,  Eunyoung Moon and James Howison. No Science Software is an Island: Collaborative Software Development Needs in Geosciences~\cite{wssspe2_gil}
\item Ted Habermann, Andrew Collette, Steve Vincena, Werner Benger, Jay Jay Billings, Matt Gerring, Konrad Hinsen, Pierre de Buyl, Mark K\"{o}nnecke, Filipe Rnc Maia and Suren Byna. The Hierarchical Data Format ({HDF}): A Foundation for Sustainable Data and Software~\cite{wssspe2_habermann}
\item Marcus Hanwell, Patrick O'Leary and Bob O'Bara. Sustainable Software Ecosystems: Software Engineers, Domain Scientists, and Engineers Collaborating for Science~\cite{wssspe2_hanwell}
\item Eric Hutton, Mark Piper, Irina Overeem, Albert Kettner and James Syvitski. Building Sustainable Software - The {CSDMS} Approach~\cite{wssspe2_hutton}
\item W. Christopher Lenhardt, Stanley Ahalt, Matt Jones, J. Aukema, S. Hampton, S. R. Hespanh, R. Idaszak and M. Schildhauer. {ISEES-WSSI} Lessons for Sustainable Science Software from an Early Career Training Institute on Open Science Synthesis~\cite{wssspe2_lenhardt}
\item James S. Spencer, Nicholas S. Blunt, William A. Vigor, Fionn D. Malone, W. M. C. Foulkes, James J. Shepherd and Alex J. W. Thom. The {H}ighly {A}ccurate {N-DE}terminant ({HANDE}) quantum {Monte Carlo} project: Open-source stochastic diagonalisation for quantum chemistry~\cite{wssspe2_spencer}
\end{itemize}

\item Policy
\begin{itemize}
\item James Howison. Retract bit-rotten publications: Aligning incentives for sustaining scientific software~\cite{wssspe2_howison}
\item Daniel Katz and Arfon Smith. Implementing Transitive Credit with {JSON-LD}~\cite{wssspe2_katz}
\item Ian Kelley. Publish or perish: the credit deficit to making software and generating data~\cite{wssspe2_kelley}
\end{itemize}

@@

Uncategorized

\begin{itemize}

\item Jory Schossau and Greg Wilson. Which Sustainable Software Practices Do Scientists Find Most Useful?~\cite{wssspe2_schossau}

>>>>

\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(affil?)}$, \\
Matthew Turk$^{(2)}$, Colin C. Venters$^{(6)}$, Nancy Wilkins-Diehr$^{(7)}$}

@@

\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}

\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}

@@

\thanks{{}$^{(7)}$ University of California-San Diego, San Diego, CA, USA}

@@

\todo{fix David's affil}

@@

The organizers then chose the soft with five groups as the one that felt most meaningful, then decided on names for the five groups, namely:
\begin{itemize}
\item Exploring Sustainability
\item Software Development Experiences
\item Credit \& Incentives
\item Reproducibility \& Reuse \& Sharing
\item Code Testing \& Code Review
\end{itemize}

@@

The contributed papers that will be discussed at the workshop follow, listed by groups (determined as described in the previous section.)

@@

\item Software Development Experiences
\begin{itemize}
\item Jordan Adams, Sai Nudurupati, Nicole Gasparini, Daniel Hobley, Eric Hutton, Gregory Tucker and Erkan Istanbulluoglu. Landlab: Sustainable Software Development in Practice ~\cite{wssspe2_adams}
\item Alice Allen and Judy Schmidt. Looking before leaping: Creating a software registry~\cite{wssspe2_allen}
\item Carl Boettiger, Ted Hart, Scott Chamberlain and Karthik Ram. Building software, building community: lessons from the {ROpenSci} project~\cite{wssspe2_boettiger}
\item Michael R. Crusoe and C.Titus Brown. Channeling community contributions to scientific software: a hackathon experience~\cite{wssspe2_crusoe}
\item Yolanda Gil,  Eunyoung Moon and James Howison. No Science Software is an Island: Collaborative Software Development Needs in Geosciences~\cite{wssspe2_gil}
\item Ted Habermann, Andrew Collette, Steve Vincena, Werner Benger, Jay Jay Billings, Matt Gerring, Konrad Hinsen, Pierre de Buyl, Mark K\"{o}nnecke, Filipe Rnc Maia and Suren Byna. The Hierarchical Data Format ({HDF}): A Foundation for Sustainable Data and Software~\cite{wssspe2_habermann}
\item Marcus Hanwell, Patrick O'Leary and Bob O'Bara. Sustainable Software Ecosystems: Software Engineers, Domain Scientists, and Engineers Collaborating for Science~\cite{wssspe2_hanwell}
\item Eric Hutton, Mark Piper, Irina Overeem, Albert Kettner and James Syvitski. Building Sustainable Software - The {CSDMS} Approach~\cite{wssspe2_hutton}
\item W. Christopher Lenhardt, Stanley Ahalt, Matt Jones, J. Aukema, S. Hampton, S. R. Hespanh, R. Idaszak and M. Schildhauer. {ISEES-WSSI} Lessons for Sustainable Science Software from an Early Career Training Institute on Open Science Synthesis~\cite{wssspe2_lenhardt}
\item Jory Schossau and Greg Wilson. Which Sustainable Software Practices Do Scientists Find Most Useful?~\cite{wssspe2_schossau}
\item James S. Spencer, Nicholas S. Blunt, William A. Vigor, Fionn D. Malone, W. M. C. Foulkes, James J. Shepherd and Alex J. W. Thom. The {H}ighly {A}ccurate {N-DE}terminant ({HANDE}) quantum {Monte Carlo} project: Open-source stochastic diagonalisation for quantum chemistry~\cite{wssspe2_spencer}
\end{itemize}

\item Credit \& Incentives
\begin{itemize}
\item James Howison. Retract bit-rotten publications: Aligning incentives for sustaining scientific software~\cite{wssspe2_howison}
\item Daniel Katz and Arfon Smith. Implementing Transitive Credit with {JSON-LD}~\cite{wssspe2_katz}
\item Ian Kelley. Publish or perish: the credit deficit to making software and generating data~\cite{wssspe2_kelley}
\end{itemize}

@@
